---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# RMETAR

<!-- badges: start -->
<!-- badges: end -->

The goal of RMETAR is to provide a METAR decoder for R users, connecting to `mdsplib` (METAR Decoder Software Package Library - https://github.com/flightaware/mdsplib) 


## Installation

~~You can install the released version of RMETAR from [CRAN](https://CRAN.R-project.org) with:~~

``` r
install.packages("RMETAR")
```

And the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("remotes")
remotes::install_github("jwijffels/RMETAR")
```


## Obtaining METAR reports

Current and historical METAR data can be obtained from various places. The current METAR report for a given airport is available at the following URL where '{station}' is the four-letter ICAO airport station code.


    https://aviationweather.gov/metar/data?ids={station}

For example, you can find the METAR for London Heathrow (ICAO EGLL) at https://aviationweather.gov/metar/data?ids=egll
    

You can also query the NOAA data service at https://aviationweather.gov/dataserver/example?datatype=metar, where you can access METARS using search strings to retrieve data in XML format


## METAR specifications


The Federal Meteorological Handbook No.1. (FMH-1 1995), which describes the U.S. standards, is available online at http://www.ofcm.gov/fmh-1/fmh1.htm

## Example


```{r}
library(RMETAR)
```

```{r}
metarcode <- "KSUU 240858Z AUTO 24018KT 10SM CLR 18/12 A2988 RMK AO2 SLPNO T01750124 58003 RVRNO"
result <- decodemetar(x = metarcode, printdecodedmetar=TRUE)
```

The decoded data is in a nested list:

```{r}
str(result, max.level = 2)
```


