---
title: "Decode METAR reports"
output: rmarkdown::html_vignette
author: Jan Wijffels
vignette: >
  %\VignetteIndexEntry{Decode METAR reports}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(RMETAR)
```



## Abstract

METAR decoder for R users, connecting to mdsplib (METAR Decoder Software Package Library)

METAR is a format for reporting weather information. A METAR weather report is predominantly used by pilots in fulfillment of a part of a pre-flight weather briefing, and by meteorologists, who use aggregated METAR information to assist in weather forecasting.

Raw METAR is the most popular format in the world for the transmission of weather data.

This R package connects to mdsplib - the official METAR Decoder Software Package Library available at http://mdsplib.sourceforge.net/ to extract all weather information from METAR reports.



## Example

```{r}
metarcode <- "KSUU 240858Z AUTO 24018KT 10SM CLR 18/12 A2988 RMK AO2 SLPNO T01750124 58003 RVRNO"
z <- decodemetar(metarcode, print = TRUE)
```

## GitHub - package repository

The development of this package is done by BNOSAC and is available on github at https://github.com/jwijffels/RMETAR